---
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
options(width = 1000)
options(tibble.width = Inf)
```

# hcop:  HGNC Comparison of Orthology Predictions (HCOP)

Human ortholog data from HGNC Comparison of Orthology Predictions (HCOP). The HGNC Comparison of Orthology Predictions (HCOP) integrates and displays the orthology assertions predicted for a specified human gene, or set of human genes, by eggNOG, Ensembl Compara, HGNC, HomoloGene, Inparanoid, NCBI Gene Orthology, OMA, OrthoDB, OrthoMCL, Panther, PhylomeDB, TreeFam and ZFIN. An indication of the reliability of a prediction is provided by the number of databases which concur. This package only contains ortholog data to _C. elegans_, chicken, fruitfly, mouse, rat, xenopus, and zebrafish. Others are available at <https://www.genenames.org/cgi-bin/hcop> via ftp at <ftp://ftp.ebi.ac.uk/pub/databases/genenames/hcop/>.

See [data-raw/hcop.R](data-raw/hcop.R) for how this data was generated.

## Installation

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("stephenturner/hcop")
```

## Usage

Get the mouse orthologs of your favorite genes

```{r}
library(hcop)
library(dplyr)

my_favorite_human_genes <- data_frame(human_symbol=c("TP53", "TNF", "EGFR", "VEGFA", "APOE", 
                                                     "IL6", "TGFB1", "MTHFR", "ESR1", "AKT1"))
my_favorite_human_genes

# Join to mouse orthologs
my_favorite_human_genes %>% 
  inner_join(mouse, by="human_symbol")

# Continue the above, but collapse all other columns down to unique entries
my_favorite_human_genes %>% 
  inner_join(mouse, by="human_symbol") %>% 
  group_by(human_symbol) %>% 
  summarize_all(funs(. %>% unique %>% paste(collapse=";")))
```


## All the data

This package only contains ortholog data to _C. elegans_, chicken, fruit fly, mouse, rat, _Xenopus_, and zebrafish. Others are available at <https://www.genenames.org/cgi-bin/hcop> via ftp at <ftp://ftp.ebi.ac.uk/pub/databases/genenames/hcop/>.

```{r}
c.elegans
chicken
fruitfly
mouse
rat
xenopus
zebrafish
```
